### 2014-11-11 tex/bisimulation.tex
Added stuff

\section{Bisimularity Relation}
Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
according to generalized symbolic execution with lazy initialization
(see the supplemental text for a precise definition of that
relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
algorithm in this paper. The principle theoretical result is the
existence of a bisimularity relation between states related on $p \rgse p^\prime$
and the states related on $q \rsym q^\prime$. A corollary is that $\rsym$ is
both sound and complete with respect to $\rgse$. Only a summary of the
proof is given due to space.

@@

The relation, $P \sqsubset q$, is readily established in the initial
state of a given program, as there is single initial state, $P_o =
\{p_o\}$, in any valid Javalite program. The initial state $\rsym$ is
then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.

>>>>

\section{Bisimularity Relation}
Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
according to generalized symbolic execution with lazy initialization
(see the supplemental text for a precise definition of that
relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
algorithm in this paper. The principle theoretical result is the
existence of a bisimilarity relation between states related on $p \rgse p^\prime$
and the states related on $q \rsym q^\prime$. A corollary is that $\rsym$ is
both sound and complete with respect to $\rgse$. Only a summary of the
proof is given due to space.

@@

The relation, $P \sqsubset q$, is readily established in the initial
state of a given program, as there is single initial state, $P_o =
\{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.
